---
title: "Developing Data Product"
subtitle: "Week 3 Assignment"
author: "Nur Seto Dimas"
date: "1 January 2020"
output: 
  ioslides_presentation: 
    highlight: haddock
    keep_md: yes
    smaller: yes
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```

## Overview  
This is an R Markdown presentation about global suicide rates in 1985 to 2016. The dataset is from [kaggle](https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016).  

## References
- United Nations Development Program. (2018). Human development index (HDI). Retrieved from http://hdr.undp.org/en/indicators/137506

- World Bank. (2018). World development indicators: GDP (current US$) by country:1985 to 2016. Retrieved from http://databank.worldbank.org/data/source/world-development-indicators#

- [Szamil]. (2017). Suicide in the Twenty-First Century [dataset]. Retrieved from https://www.kaggle.com/szamil/suicide-in-the-twenty-first-century/notebook

- World Health Organization. (2018). Suicide prevention. Retrieved from http://www.who.int/mental_health/suicide-prevention/en/ 



## Data Preprocessing
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)

# load dataset
plotdata <- read.csv(file = "master.csv")

# tidying up dataset
plotdata <- plotdata %>% 
        rename(country.name = ï..country) %>%
        as.data.frame()

plotdata_summary <- plotdata %>%
        group_by(year) %>%
        summarize(population = sum(population),
                  suicides = sum(suicides_no),
                  suicides_per_100k = (suicides / population) * 100000)
```


## Plotly
```{r plot code, eval=FALSE, message=FALSE, warning=FALSE}
# Create plot
p <- plot_ly(data = plotdata_summary, 
             x = ~year, y = ~suicides_per_100k, 
             mode = "lines+markers") %>%
        layout(title = "Global Suicides Trends per 100k")
```

## Plotly
```{r plot, message=FALSE, warning=FALSE, echo=FALSE}
# Create plot
p <- plot_ly(data = plotdata_summary, x = ~year, y = ~suicides_per_100k, mode = "lines+markers") %>%
        layout(title = "Global Suicides Trends per 100k")
p
```
